---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!--
[![Build Status](https://travis.metrumrg.com/yoni/texblocks.svg?token=tfrDuc83e84K9CqJKyCs&branch=master)](https://travis.metrumrg.com/yoni/texblocks)
--->

`r if(knitr::opts_knit$get('rmarkdown.pandoc.to')=='html')
'[![Build Status](https://travis.metrumrg.com/yoni/texblocks.svg?token=tfrDuc83e84K9CqJKyCs&branch=master)](https://travis.metrumrg.com/yoni/texblocks)'`

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README",
  warning = FALSE,
  message = FALSE
)
```

# texblocks

## Load Library

```{r}
library(texblocks)
library(texPreview)
```
 
```{r,include=FALSE}
tex_opts$set(returnType= 'html',
             resizebox = FALSE,
             fileDir = 'tools/README',
             opts.html = list(width='25%',height='25%'))

tex_opts$append(list(cleanup='tex'))
```

## Initialize basic texblocks

### Single blocks

```{r}
x <- as.tb('$\\alpha$')
y <- as.tb('aaa')
z <- as.tb('bbb')

```

### Vectors

```{r}
k0 <- rep(x,3)
k0

k1 <- lapply(1:3,as.tb)
k1

k2 <- lapply(4:6,as.tb)
k2
```

## Operators 

### Horizontal Concatentation

```{r}
x1 <- x+y+z
x1
```

### Vertical Concatentation

```{r}
x/y
```

## Creating a tabular object

```{r}
x1%>%
  texblocks::tabular()

x1%>%
  texblocks::tabular(align = 'c|c|c')
```

## Compiling with texPreview

```{r, echo=TRUE,results='asis'}
x1%>%
  texblocks::tabular()%>%
  texPreview::texPreview(stem = "tb1")

```

### Combining blocks

```{r}
x1 + x1
```
 
```{r}
x2 <- x1 / x1
x2 + x2
```
 
```{r, echo=TRUE,results='asis'}
x2%>%
  texblocks::tabular()%>%
  texPreview::texPreview(stem = "tb2")

```

### Unequal blocks
 
```{r}
x3 <- x2/x2
x2 + x3
```

```{r, echo=TRUE,results='asis'}
x3%>%
  texblocks::tabular()%>%
  texPreview::texPreview(stem = "tb3")

```

```{r, echo=TRUE,results='asis'}
(x2 / x2)%>%
  texblocks::tabular()%>%
  texPreview::texPreview(stem = "tb4")

```
 
```{r, echo=TRUE,results='asis'}
(x2 + x3)%>%
  texblocks::tabular()%>%
  texPreview::texPreview(stem = "tb5")

```
 
```{r, echo=TRUE,results='asis'}
(x3 + x3)%>%
  texblocks::tabular()%>%
  texPreview::texPreview(stem = "tb6")

```

### Reducing vectors

(Not sure if this needs to be wrapped into a single function instead of having users apply reduce)

```{r}
purrr::reduce(k1,`+`)

k <- purrr::reduce(k1,`+`) / purrr::reduce(k2,`+`)

k
```

```{r, echo=TRUE,results='asis'}
k %>%
  texblocks::tabular()%>%
  texPreview::texPreview(stem = "tb7")

``` 

## Converting to a data.frame

```{r}
as.data.frame( x2 + x3 )
```


```{r, echo=TRUE,results='asis'}

title <- c('param',sprintf('col%s',1:5))%>%
  purrr::map(as.tb)%>%
  purrr::reduce(`+`)

title / (x2 + x3)%>%
  tabular(align = '|c|ccccc|')%>%
  texPreview::texPreview(stem = "tb8")

```

## hline

Add hlines into the table using `hline`.

hline expects the lines to add hline to, where 0 is a possible value for lines which a line will be added to the top of the table. When lines are left empty then all the lines will have hline attached to them.

```{r,echo=TRUE,results='asis'}
title / (x2 + x3)%>%
  hline()%>%
  tabular(align = '|c|ccccc|')%>%
  texPreview::texPreview(stem = "tb9")

title / (x2 + x3)%>%
  hline(lines = c(2,3))%>%
  tabular(align = '|c|ccccc|')%>%
  texPreview::texPreview(stem = "tb10")
```

## cline

Add clines into the table using `hline`. 

Define where to put in the clines with a `spec` object. The spec can be either a list or data.frame either of which containing the elements `line,i,j`, where line is the line to apply the cline, i,j is the starting end ending columns respectivley. 

cline expects the lines to add hline to, where 0 is a possible value for lines which a line will be added to the top of the table. 

```{r}
l <- list(c(line=1,i=2,j=3),c(line=2,i=1,j=2),c(line=3,i=2,j=3))
d <- data.frame(line=1:3,i=c(1,2,3),j=c(1,2,3))
```

```{r,echo=TRUE,results='asis'}
purrr::reduce(rep(x1,4),`/`)%>%
  cline(l)%>%
  tabular()%>%
  texPreview::texPreview(stem = "tb11")

purrr::reduce(rep(x1,4),`/`)%>%
  cline(d)%>%
  tabular()%>%
  texPreview::texPreview(stem = "tb12")

```

you can also combine hline and cline in a pipe

```{r,echo=TRUE,results='asis'}
purrr::reduce(rep(x1,4),`/`)%>%
  cline(d)%>%
  hline(c(0,4))%>%
  tabular()%>%
  texPreview::texPreview(stem = "tb13")

```

## Multicol/Multirow

```{r,echo=TRUE,results='asis'}
title <- as.tb('param') + multicol('vals',3,'c|')

tab <- title / (multirow('$\\beta$',2) + k)

tab%>%
  tabular(align = '|cccc|')%>%
  texPreview::texPreview(stem='tb14')

```


```{r,include=FALSE}
file.copy('tools',to = 'docs',overwrite = TRUE,recursive = TRUE)
```

# Design/Specs

Building blocks for TeX tables

## Idea

Assemble LaTeX tabular environments using simple operations.

This would enable us to create any table layout with a consistent user API.

Defining a new class of R element `tabular` that is the basic structure of the language.

## Proposed Syntax

Defining a new class of R element `tb` that is the basic structure of the language.

### Joining elements

Let `t1` and `t2` be two objects of class tb.

|  |   |
|:--:|:--:|
| `t1 + t2`  |`r '\u2b1b'` `r '\u2b1b'`|


|  |   |
|:--:|:--:|
||`r '\u2b1b'`|
|`t1 / t2`||
||`r '\u2b1b'`|


Using this language creating a table can be broken down to cell level

`t1 =(``r '\u2b1b'`` + ``r '\u2b1b'`` + ``r '\u2b1b'``) / (``r '\u2b1b'`` + ``r '\u2b1b'`` + ``r '\u2b1b'``)`

would be translated to 

```
1 & 2 & 3 \\
4 & 5 & 6
```

making their combination a natural extension

`t1 + t1`

would translate to 

```
1 & 2 & 3 & 1 & 2 & 3 \\
4 & 5 & 6 & 1 & 2 & 3
```

### Mutations

  - multirow
  - multicolumn
  
### Aesthetics

A set of aesthetic elements can be defined to control the table and cell level attributes, eg

  - font: colour, size, face
  - background colour
  - grid: hline, cline
