---
title: "Aesthetics"
author: "Jonathan Sidi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r}
library(texblocks)
library(texPreview)

```
 
```{r,include=FALSE}
tex_opts$set(returnType = knitr::opts_knit$get('rmarkdown.pandoc.to'))
tex_opts$append(list(cleanup='tex'))
```

```{r}
x <- as.tb('$\\alpha$')
y <- as.tb('aaa')
z <- as.tb('bbb')
```

```{r}
x1 <- x + y + z
x2 <- x1 / x1 # 2x3 object
x3 <- x2 / x2 # 4x3 object

k1 <- lapply(1:3,as.tb)
k2 <- lapply(4:6,as.tb)

k <- purrr::reduce(k1,`+`) / purrr::reduce(k2,`+`)

title <- c('param',sprintf('col%s',1:5))%>%
  purrr::map(as.tb)%>%
  purrr::reduce(`+`)

```

## hline

Add hlines into the table using `hline`.

hline expects the lines to add hline to, where 0 is a possible value for lines which a line will be added to the top of the table. When lines are left empty then all the lines will have hline attached to them.

```{r hline}
(title / (x2 + x3))%>%
  hline()%>%
  tabular()%>%
  texPreview::texPreview()

```
 
```{r hline2}
(title / (x2 + x3))%>%
  hline(lines = c(2,3))%>%
  tabular()%>%
  texPreview::texPreview()

```

## cline

Add clines into the table using `hline`. 

Define where to put in the clines with a `spec` object. The spec can be either a list or data.frame either of which containing the elements `line,i,j`, where line is the line to apply the cline, i,j is the starting end ending columns respectivley. 

cline expects the lines to add hline to, where 0 is a possible value for lines which a line will be added to the top of the table. 

```{r}
l <- list(c(line=1,i=2,j=3),c(line=2,i=1,j=2),c(line=3,i=2,j=3))
d <- data.frame(line=1:3,i=c(1,2,3),j=c(1,2,3))
```

```{r cline}
purrr::reduce(rep(x1,4),`/`)%>%
  cline(l)%>%
  tabular()%>%
  texPreview::texPreview()

purrr::reduce(rep(x1,4),`/`)%>%
  cline(d)%>%
  tabular()%>%
  texPreview::texPreview()

```

you can also combine hline and cline in a pipe

```{r lines_pipe}
purrr::reduce(rep(x1,4),`/`)%>%
  hline(c(0,4))%>%
  cline(d)%>%
  tabular()%>%
  texPreview::texPreview()
```

## Multicol/Multirow

```{r multirow,echo=TRUE,results='asis'}
title <- as.tb('param') + multicol('vals',3,'c')

(title / (multirow('$\\beta$',2) + k))%>%
  tabular()%>%
  texPreview::texPreview()

```
