---
title: "Recasting texblocks"
author: "Jonathan Sidi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Recasting texblocks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(texblocks)
library(texPreview)
```

```{r,include=FALSE}
tex_opts$set(returnType = 'html')
tex_opts$append(list(cleanup='tex'))
```
# Recasting from raw tex

## Original tex Code

can be with or without tabular wrapper

```{r remedy001}

x <- '\\begin{tabular}{l|cccccccccc}
number of flips& 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 \\\\
number of heads& 8  &  8 &  9 & 10 & 10 & 10 & 10 & 10 & 10 & 11 \\\\\\hline
proportion& .73 & .67 & .69 & .71 & .67 &  .63 & .59 & .56 & .53 & .55
\\end{tabular}'

```

```{r remedy002}

x <- 'number of flips& 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 \\\\
number of heads& 8  &  8 &  9 & 10 & 10 & 10 & 10 & 10 & 10 & 11 \\\\\\hline
proportion& .73 & .67 & .69 & .71 & .67 &  .63 & .59 & .56 & .53 & .55'

```

## Recast to texblock

```{r}
x <- x%>%as.tb()
```

## Recast to data.frame

```{r remedy003}

x%>%
  as.data.frame()

```

Use `type.convert()` to set column class in matrix

```{r remedy004}

x%>%
  as.data.frame(convert = TRUE)

```

## manipulations

### gather the columns using tidyr

```{r remedy005}

x%>%
  as.data.frame(convert = TRUE)%>%
  tidyr::gather(col,val,-1)

```

#### transponse as a texblock then convert to a data.frame

```{r remedy006}

x%>%
  t()%>%
  as.data.frame()

```

## Preview table using texPreview

```{r remedy007}

x%>%
  t()%>%
  hline()%>%
  tabular(align = '|c|c|c|')%>%
  texPreview::tex_preview()

```

# Recasting to and from a Sparse Matrix

## Create Block Matrix

```{r remedy008}

mat <- Matrix::bdiag(
  Matrix::Diagonal(2), 
  matrix(1:3, 3,4), 
  diag(3:2)
)

mat
```

## Convert a matrix to a texblock

```{r remedy009}

x <- mat %>% as.tb()

x

```

## crop

extract subset of the texblock by index

```{r remedy010}

x%>%crop(1:2,1:2) # extract smaller tb from rows 1:2 columns 1:2
x%>%crop(3:5,3:6) # extract smaller tb from rows 3:5 columns 3:6
x%>%crop(6:7,7:8) # extract smaller tb from rows 6:7 columns 7:8

```

## harvest

extract subsets of the texblock using lists , i.e. blocks of tb's by blocks of the matrix

```{r remedy011}

x1 <- x%>%
  harvest(
    list(1:2,3:5,6:7),
    list(1:2,3:6,7:8)
  )

x1


```

Back to the original Sparse Matrix

```{r remedy012}

x1%>%
  purrr::map(as.matrix)%>% #convert back to list of matrices
  Matrix::bdiag() # convert back to original block matrix

```
